---
title: "All Geocoded LA"
author: "Bill Lang"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
library(tidygeocoder)
```

Loading in our data from the Rproject.

```{r}
load(file = "NY.RData")
ny
```

we clean up some of the columns that contain information on the address of a row and assign each the best we can without digging too deep into the data itself.

```{r}
#Removing right adjustment
ny$Column.Location <- trimws(ny$Column.Location, which = c("right"))
#Manual Cleaning Some of the observations
ny$Column.Location <- sub("nj","new jersey", ny$Column.Location)
ny$Column.Location <- sub("ny","new york", ny$Column.Location)
ny$Column.Location <- sub("li","long island", ny$Column.Location)
ny$Column.Location <- sub("-","", ny$Column.Location)
ny$Column.Location <- sub("&","", ny$Column.Location)
ny$Column.Location <- sub(" ","", ny$Column.Location)
ny$Column.Location <- sub("#","", ny$Column.Location)
```

We can see that only 40 rows are missing all of there location data.

```{r}
ny$Area <- tolower(ny$Area)
ny$Street <- tolower(ny$Street)
ny$Column.Location <- tolower(ny$Column.Location)

ny <- ny %>% unite(Address1, c("Hse.No","Street","Column.Location"), sep = " ",remove = FALSE)
ny <- ny %>% unite(Address2, c("Area","Column.Location"), sep = " ",remove = FALSE)

ny$Address1 <- trimws(ny$Address1, which = c("right"))
ny$Address2 <- trimws(ny$Address2, which = c("right"))

ny <- ny %>% mutate(Address = ifelse(Address1 != "", as.character(Address1),  as.character(Address2)))
ny %>% filter(Address == "")
ny <- ny %>% select(-Address1,-Address2, -X.1, -X)
```



We can clean the Coarse.geo column as we create it.

```{r}
ny$Coarse.Geo <- tolower(ny$Column.Location)
#More column.location cleaning here
ny$Coarse.Geo <- trimws(ny$Coarse.Geo, which = c("right"))
ny$Coarse.Geo <- tolower(ny$Coarse.Geo)
ny$Coarse.Geo <- sub("nj","new jersey", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("ny","new york", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("li","long island", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("-","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("&","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub(" ","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("county","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub(" state","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("queens long island","queens", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("queenslongisland","queens", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("queensand long island","queens", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("brooklynlongisland","brooklyn", ny$Coarse.Geo)
ny$Coarse.Geo <- sub(" st","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("newengland","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("manhattanbronx","manhattan", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("ville","", ny$Coarse.Geo)
ny$Coarse.Geo <- sub("brooklynqueens","brooklyn", ny$Coarse.Geo)
```

Coarse.geo is the calculated column, we can create that manually with the new york data first with the following pattern.

```{r}
#Saying that if it follows a certain pattern it is added to the new calculated column

pattern3 <- c("manhattan|westchester|newjersey|westside|eastside|queens|longisland|brooklyn|nassausuffolk|connecticut|bronx|queens& long island|newyork|westchestercounty|queenslongisland|statenisland")
ny <- ny %>% mutate(Coarse.Geo = ifelse(
  grepl(pattern3, Column.Location, ignore.case = TRUE), as.character(Column.Location), 1))
```


Now we send the entire file through this Open Street Map API (using the package tidygeocoder) and collect the results
 
```{r}
geocodedNY <- tidygeocoder::geocode(.tbl = ny, address = Address, method = "osm", lat = latitude, long = longitude)
save(geocodedNY, file = "allNY.RData")
```

```{r}
load(file = "allNY.RData")
geocodedNY
```




We can create two data sets of our results that were found and are withing a reasonable region of the city and results were not found and are well outside the city.

```{r}
incorrectMatches <- geocodedNY %>% filter((is.na(latitude) | (latitude < 38) | (latitude > 44) | (longitude < -78) | (longitude > -71)) )
```

```{r}
correctMatches <- geocodedNY %>% filter(!(is.na(latitude) | (latitude < 38) | (latitude > 44) | (longitude < -78) | (longitude > -71)) )
```

```{r}
correctMatches
incorrectMatches
```





We can use the ggmap package to map the results over all New York.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
map <- get_map(location = 'New York', zoom = 7, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = correctMatches, mapping = aes(x = longitude, y = latitude, color = factor(Column.Location)), size = 1) + theme(legend.position = "none")
```





