---
title: "Training Random Forest LA"
author: "Bill Lang"
date: "8/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```


This first half will construct a random forest model on the 15,713 observations that have a full address and an area specification in the top 50.

Reading in file.

```{r}
load(file = "cleanLA.RData")
LAData
```

Removing areas with no information. 

```{r}
LAData <- LAData %>% filter(editArea != "") 
```

Finding the top 50 labeled areas.

```{r}
LAData$editArea <- tolower(LAData$editArea)
tbl <- LAData %>% group_by(editArea) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreasLA <- tbl[1:50,]$editArea
listOfAreasLA
save(listOfAreasLA, file = "AreasLA.RData")
```

Find the observations with a top 50 area. 

```{r}
LADataAddress <- LAData %>% filter(editArea %in% listOfAreasLA) 
LADataAddress$editArea <- as.factor(LADataAddress$editArea)
```

This model is built on a random shuffle of the data and validated by holding out 20% of the dataset. 
 
```{r}
modelData <- LADataAddress 
set.seed(343)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.9)
LATrain <- modelData[train,]
LaTest <- modelData[-train,]

```


```{r}
bag <- randomForest(editArea ~ latitude + longitude + capitalizedPrice, data = LATrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(bag, newdata = LaTest)
misclassRate <- mean(yhat.rf != LaTest$editArea)
misclassRate

importance(bag, class = 1)
importance(bag, type = 2)
```

```{r}
predicted <- cbind(yhat.rf, LaTest)
predicted
```

We can then map the results using the ggmaps package below to manuely search for any errors.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
map <- get_map(location = 'Los Angeles', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(editArea)), size = 1)+ theme(legend.position = "none")
```


Full Model

Using all the available data we construct a full model to use for the rest of the analysis. 

```{r}
fullModel <- randomForest(Area ~ latitude + longitude + Year + Total.rooms + Price.type + capitalizedPrice, data = firstGeocodeFile, ntree = 1000, mtry = 2, importance = TRUE)
```

```{r}
importance(fullModel, type = 1)
```































The next lines of code investigate how well this model performs on the 8871 observations that don't have a house number. 

First we can re-clean the data from earlier to get the 8,871 observations without a good house number.

```{r}
load("cleanBoston.RData")
```

```{r}
bostonData <- bostonData %>% filter(Area != "")
```

```{r}
bostonData$Area <- tolower(bostonData$Area)
bostonData <- bostonData %>% filter(Area %in% listOfAreas)
bostonAddress <- bostonData %>% unite(Address, c("Hse.No","Street","Area"), sep = " ",remove = FALSE)
bostonAddress$Address <- paste(bostonAddress$Address, " , MA")
```

```{r}
bostonAddress <- bostonAddress %>% filter(Area != "") %>% filter((Street != "") | (Cross.Street != "")) %>% filter(Hse.No == "")
```

Cleaning the data same as before.

```{r}
geocodeFileNoHse <- geocodeFileNoHse %>% filter(!is.na(latitude))
geocodeFileNoHse$Area <- as.factor(geocodeFileNoHse$Area)

geocodeFileNoHse <- geocodeFileNoHse %>% filter(latitude < 43) %>% filter(latitude > 42) %>% filter(longitude > -71.75)

```


Predict the data from the previous model and get another misclassification rate. 

```{r}
yhat.rf <- predict(fullModel, newdata = geocodeFileNoHse)
predicted <- cbind(yhat.rf, geocodeFileNoHse)
predicted

misclassNoHse <- mean(yhat.rf != geocodeFileNoHse$Area)
misclassNoHse
```

Mapping the predicted results. 

```{r}
map <- get_map(location = 'Boston', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = predicted, mapping = aes(x = longitude, y = latitude, color = factor(yhat.rf)), size = 1)
```

