---
title: "Training Random Forest LA"
author: "Bill Lang"
date: "8/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```


This first half will construct a random forest model on the 15,713 observations that have a full address and an area specification in the top 50.

Reading in file.

```{r}
load(file = "cleanLA.RData")
LAData 
```

Removing areas with no information.

```{r}
LAData <- LAData %>% filter(editArea != "")
dim(LAData)
```

Finding the top 50 labeled areas.

```{r}
LAData$editArea <- tolower(LAData$editArea)
tbl <- LAData %>% group_by(editArea) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreasLA <- tbl[1:49,]$editArea
listOfAreasLA
save(listOfAreasLA, file = "AreasLA.RData")
```

Find the observations with a top 50 area. 

```{r}
LADataAddress <- LAData %>% filter(editArea %in% listOfAreasLA) 
LADataAddress$editArea <- as.factor(LADataAddress$editArea)
dim(LADataAddress)
```

This model is built on a random shuffle of the data and validated by holding out 20% of the dataset. 
 
```{r}
modelData <- LADataAddress 
set.seed(343)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.9)
LATrain <- modelData[train,]
LaTest <- modelData[-train,]
```


```{r}
bag <- randomForest(editArea ~ latitude + longitude + capitalizedPrice, data = LATrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(bag, newdata = LaTest)
misclassRate <- mean(yhat.rf != LaTest$editArea)
misclassRate

importance(bag, class = 1)
importance(bag, type = 2)
```

```{r}
predicted <- cbind(yhat.rf, LaTest)
predicted
```

We can then map the results using the ggmaps package below to manuely search for any errors.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
map <- get_map(location = 'Los Angeles', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(editArea)), size = 1)+ theme(legend.position = "none")
```


Full Model

Using all the available data we construct a full model to use for the rest of the analysis. 

```{r}
fullModel <- randomForest(editArea ~ latitude + longitude + capitalizedPrice, data = modelData, ntree = 1000, mtry = 2, importance = TRUE)
```

```{r}
importance(fullModel, type = 1)
```





























