---
title: "Training Random Forest"
author: "Bill Lang"
date: "7/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```


This first half will construct a random forest model on the 15,713 observations that have a full address and an area specification in the top 50.

Reading in file.

```{r}
load(file = "cleanNY.RData")
NYData
```

Removing areas with no information. 

```{r}
NYData <- NYData %>% filter(Column.Location != "") 
```

Finding the top 15 labeled areas.

```{r}
NYData$Column.Location <- tolower(NYData$Column.Location)

#More column.location cleaning here


tbl <- NYData %>% group_by(Column.Location) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreasNY <- tbl[1:10,]$Column.Location
listOfAreasNY
save(listOfAreasNY, file = "NYAreas.RData")
```

Find the observations with a top 50 area. 

```{r}
NYData <- NYData %>% filter(Column.Location %in% listOfAreasNY) 
```

Finding the 15,713 observations with full addresses.

```{r}
NYData <- NYData %>% filter(!is.na(latitude))
NYData$Column.Location <- as.factor(NYData$Column.Location)
```

Model Building on the first batch

This model is built on a random shuffle of the data and validated by holding out 20% of the dataset. 
 
```{r}
NYData
modelData <- NYData 
set.seed(343)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.8)
dataTrain <- modelData[train,]
dataTest <- modelData[-train,]
```


```{r}
bag <- randomForest(Column.Location ~ latitude + longitude + Year + capitalizedPrice, data = dataTrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(bag, newdata = dataTest)
misclassRate <- mean(yhat.rf != dataTest$Column.Location)
misclassRate
```

```{r}
predicted <- cbind(yhat.rf, dataTest)
predicted
```

We can then map the results using the ggmaps package below to manuely search for any errors.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
map <- get_map(location = 'Boston', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(Area)), size = 1)
```


Full Model

Using all the available data we construct a full model to use for the rest of the analysis. 

```{r}
fullModel <- randomForest(Column.Location ~ latitude + longitude + Year + capitalizedPrice, data = NYData, ntree = 500, mtry = 2, importance = TRUE)
```






























The next lines of code investigate how well this model performs on the 8871 observations that don't have a house number. 

First we can re-clean the data from earlier to get the 8,871 observations without a good house number.

```{r}
load("cleanBoston.RData")
```

```{r}
bostonData <- bostonData %>% filter(Area != "")
```

```{r}
bostonData$Area <- tolower(bostonData$Area)
bostonData <- bostonData %>% filter(Area %in% listOfAreas)
bostonAddress <- bostonData %>% unite(Address, c("Hse.No","Street","Area"), sep = " ",remove = FALSE)
bostonAddress$Address <- paste(bostonAddress$Address, " , MA")
```

```{r}
bostonAddress <- bostonAddress %>% filter(Area != "") %>% filter((Street != "") | (Cross.Street != "")) %>% filter(Hse.No == "")
```

Cleaning the data same as before.

```{r}
geocodeFileNoHse <- geocodeFileNoHse %>% filter(!is.na(latitude))
geocodeFileNoHse$Area <- as.factor(geocodeFileNoHse$Area)

geocodeFileNoHse <- geocodeFileNoHse %>% filter(latitude < 43) %>% filter(latitude > 42) %>% filter(longitude > -71.75)

```


Predict the data from the previous model and get another misclassification rate. 

```{r}
yhat.rf <- predict(fullModel, newdata = geocodeFileNoHse)
predicted <- cbind(yhat.rf, geocodeFileNoHse)
predicted

misclassNoHse <- mean(yhat.rf != geocodeFileNoHse$Area)
misclassNoHse
```

Mapping the predicted results. 

```{r}
map <- get_map(location = 'Boston', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = predicted, mapping = aes(x = longitude, y = latitude, color = factor(yhat.rf)), size = 1)
```




