---
title: "Training Random Forest"
author: "Bill Lang"
date: "7/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```


Reading in cleaned data file.

```{r}
load(file = "cleanNY.RData")
NYData
```




We can grab the top 12 by frequency from our coarse geography information. 

```{r}
tbl <- NYData %>% group_by(Coarse.Geo) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreasNY <- tbl[1:12,]$Coarse.Geo

listOfAreasNY <- listOfAreasNY[listOfAreasNY != "newyork"]

#save(listOfAreasNY, file = "NYAreas.RData")
load(file = "NYAreas.RData")
```





Find the observations with an area inside of the listOfAreas list. 

```{r}
NYData <- NYData %>% filter(Coarse.Geo %in% listOfAreasNY) 
```

```{r}
NYData$Coarse.Geo <- as.factor(NYData$Coarse.Geo)
```








We can now build and test a model based on the data that we know to be true (data that was contained in the listOfAreas list).
 
```{r}
NYData
modelData <- NYData 
set.seed(343)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.8)
dataTrain <- modelData[train,]
dataTest <- modelData[-train,]
```

```{r}
randomForestModel <- randomForest(Coarse.Geo ~ latitude + longitude + Year + capitalizedPrice, data = dataTrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(randomForestModel, newdata = dataTest)
misclassRate <- mean(yhat.rf != dataTest$Coarse.Geo)
misclassRate
```

```{r}
predicted <- cbind(yhat.rf, dataTest)
predicted
```




We can map the results using the ggmaps package below to manually search for any obvious errors. 

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
map <- get_map(location = 'New York', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')

ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(Coarse.Geo)), size = 1)

ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(Column.Location)), size = 1) +
  theme(legend.position = "none")

```





Using all the available data we have we construct a full model to use for the classification of the points that we don't know the location of.

```{r}
fullModel <- randomForest(Coarse.Geo ~ latitude + longitude + Year + capitalizedPrice, data = NYData, ntree = 500, mtry = 2, importance = TRUE)
```




















