---
title: "Cleaning and Geocoding"
author: "Bill Lang"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
library(tidygeocoder)
```


This first half will construct a random forest model on the 15,713 observations that have a full address and an area specification in the top 50.

Reading in file.

```{r}
#save(boston, file = "boston.RData")
load(file = "boston.RData")
boston
```

Removing areas with no information. 

```{r}
boston <- boston %>% filter(Area != "") 
```

Finding the top 50 labeled areas.

```{r}
boston$Area <- tolower(boston$Area)
tbl <- boston %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreas <- tbl[1:50,]$Area
listOfAreas
save(listOfAreas, file = "Areas.RData")
```

Find the observations with a top 50 area. 

```{r}
boston <- boston %>% filter(Area %in% listOfAreas) 
bostonAddress <- boston %>% unite(Address, c("Hse.No","Street","Area"), sep = " ",remove = FALSE)
bostonAddress$Address <- paste(bostonAddress$Address, ", MA")
```

Finding the 15,713 observations with full addresses.

```{r}
bostonAddress <- bostonAddress %>% filter((Street != "") | (Cross.Street != "")) %>% filter(Hse.No != "")
```

Geocoding those addresses and saving them to a file in the project (to circumvent geocoding again)
 
```{r}
#This takes hours and doesn't need run again
#geocodeFileFull <- tidygeocoder::geocode(.tbl = bostonAddress, address = Address, method = "osm", lat = latitude, long = longitude)
#firstGeocodeFile <- geocodeFileFull
```

Saving and loading the geocoding data for easy recreation. 

```{r}
save(firstGeocodeFile, file = "first.RData")
load(file = "first.RData")
firstGeocodeFile
```

Filtering outliers in the geocoding process. These results were so far outside of Boston they are being treated as failed geocoding result and not considered.

```{r}

firstGeocodeFile$Area <- as.factor(firstGeocodeFile$Area)

firstGeocodeFile <- firstGeocodeFile %>% filter(!is.na(latitude))
firstGeocodeFile <- firstGeocodeFile %>% filter(latitude < 43) %>% filter(latitude > 42) %>% filter(longitude > -71.75)

```

Preparing the dataset for a model. Shfiting all character variables to lowercase and set to factors. The average total number of rooms is 5 and is used to replace the few NAs in that column without losing much information.  

```{r}
firstGeocodeFile$Price.type <- tolower(firstGeocodeFile$Price.type)
firstGeocodeFile$Price.type <- as.factor(firstGeocodeFile$Price.type)

firstGeocodeFile$Type <- tolower(firstGeocodeFile$Type)
firstGeocodeFile$Type <- as.factor(firstGeocodeFile$Type)

firstGeocodeFile$Column <- tolower(firstGeocodeFile$Column)
firstGeocodeFile$Total.rooms <- as.integer(firstGeocodeFile$Total.rooms)

#5 is the mean of totalrooms
firstGeocodeFile <- firstGeocodeFile %>% mutate(Total.rooms = replace_na(Total.rooms,5))
```

Saving this dataset as ```trainingData.RData```, its then reloaded in the ```Random Forest Scripts``` file.


```{r}
trainingData <- firstGeocodeFile
save(trainingData, file = "trainingData.RData")
```




The next lines of code investigate how well this model performs on the 8871 observations that don't have a house number. 

First we can re-clean the data from earlier to get the 8,871 observations without a good house number.

```{r}
load("boston.RData")
```

```{r}
boston <- boston %>% filter(Area != "")
```

```{r}
boston$Area <- tolower(boston$Area)
boston <- boston %>% filter(Area %in% listOfAreas)
bostonAddress <- boston %>% unite(Address, c("Hse.No","Street","Area"), sep = " ",remove = FALSE)
bostonAddress$Address <- paste(bostonAddress$Address, " , MA")

```

```{r}
bostonAddress <- bostonAddress %>% filter(Area != "") %>% filter((Street != "") | (Cross.Street != "")) %>% filter(Hse.No == "")
```

Geocoding and saving the files same as before. 
 
```{r}
#geocodeFileFullno <- tidygeocoder::geocode(.tbl = bostonAddress, address = Address, method = "osm", lat = latitude, long = longitude)
#geocodeFileNoHse <- geocodeFileFullno

save(geocodeFileNoHse, file = "second.RData")
load(file = "second.RData")
geocodeFileNoHse
```

Cleaning the data same as before.

```{r}
geocodeFileNoHse <- geocodeFileNoHse %>% filter(!is.na(latitude))
geocodeFileNoHse$Area <- as.factor(geocodeFileNoHse$Area)

geocodeFileNoHse <- geocodeFileNoHse %>% filter(latitude < 43) %>% filter(latitude > 42) %>% filter(longitude > -71.75)

```

```{r}
geocodeFileNoHse <- geocodeFileNoHse %>% filter(Area %in% listOfAreas)
bostonArea <- geocodeFileNoHse

bostonArea$Price.type <- tolower(bostonArea$Price.type)
bostonArea$Price.type <- as.factor(bostonArea$Price.type)

bostonArea$Type <- tolower(bostonArea$Type)
bostonArea$Type <- as.factor(bostonArea$Type)


bostonArea$Column <- tolower(bostonArea$Column)
bostonArea$Total.rooms <- as.integer(bostonArea$Total.rooms)

geocodeFileNoHse <- bostonArea

#5 is the mean of totalrooms
geocodeFileNoHse <- geocodeFileNoHse %>% mutate(Total.rooms = replace_na(Total.rooms,5))
```

Again, this file is saved and reloaded in the ```Random Forest Scripts``` page.

```{r}
save(geocodeFileNoHse, file = "geocodeFileNoHse.RData")
```










Next we can take the 37,506 observations that aren't inside the top 50 regions, predict the most likely region to classify them in, and investigate if the results seem correct.

```{r}
load("boston.RData")
```

```{r}
boston$Area <- tolower(boston$Area)
boston <- boston %>% filter(!(Area %in% listOfAreas))
bostonAddress <- boston %>% unite(Address, c("Hse.No","Street","Area"), sep = " ",remove = FALSE)
bostonAddress$Address <- paste(bostonAddress$Address, " , MA")

```

Geocoding and saving the files same as before. 
 
```{r}
#geocodeFileClassify <- tidygeocoder::geocode(.tbl = bostonAddress, address = Address, method = "osm", lat = latitude, long = longitude)
```


```{r}
load(file = "third.RData")
geocodeFileClassify
```

```{r}
geocodeFileClassify <- geocodeFileClassify %>% filter(!is.na(latitude))
geocodeFileClassify$Area <- as.factor(geocodeFileClassify$Area)
```

```{r}
geocodeFileClassify$Price.type <- tolower(geocodeFileClassify$Price.type)
geocodeFileClassify <- geocodeFileClassify %>% filter(Price.type != "income")
geocodeFileClassify$Price.type <- as.factor(geocodeFileClassify$Price.type)

geocodeFileClassify$Type <- tolower(geocodeFileClassify$Type)

geocodeFileClassify$Column <- tolower(geocodeFileClassify$Column)
geocodeFileClassify$Type <- as.factor(geocodeFileClassify$Type)
geocodeFileClassify$Total.rooms <- as.integer(geocodeFileClassify$Total.rooms)

geocodeFileClassify <- geocodeFileClassify

#5 is the mean of totalrooms
geocodeFileClassify <- geocodeFileClassify %>% mutate(Total.rooms = replace_na(Total.rooms,5))



```

```{r}
missingArea<- geocodeFileClassify
save(missingArea, file = "missingArea.RData")
```





