---
title: "All Geocoded DC"
author: "Bill Lang"
date: "11/1/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
```


```{r}
load(file = "DC.RData")
load(file = "DChandcheck.RData")
```


```{r}
DC = DC[1:93879,] 

DC 
DChandcheck


DC %>% filter(Area != "")
DC %>% group_by(Column) %>% summarise(count = n()) %>% arrange(desc(count))
DC %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

#70,785 with and 63,725 without area, 

DChandcheck <- DChandcheck %>% mutate(Area = ï..Area) %>% select(Area,State) %>% distinct() %>% filter(State != "")

DChandcheck %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

DC <- DC %>% mutate(Area = tolower(Area)) %>% left_join(DChandcheck, by = 'Area') 
DC %>% filter(is.na(State))
```


```{r}
DC$Column <- tolower(DC$Column)
DC$Column <- gsub("[.]", "", DC$Column)
DC$Column <- trimws(DC$Column)

DC$Area <- tolower(DC$Area)
DC$Area <- gsub("[.]", "", DC$Area)
DC$Area <- trimws(DC$Area)

md = c("maryland|md|montgomery|prince george's|mont|prince georges|prince george|bethesda|silver spring|college park|prince geo|princegeo|princ geo|annapolis|chevy chase|rockville|gaithersburg")
va = c("virginia|va|alexandria|fairfax|arlington|falls church")
dc = c("dc|d c|district of columbia|washington|district columbia|georgetown")

DC <- DC %>% mutate(State = ifelse(grepl(md, Column, ignore.case = TRUE), "MD", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(va, Column, ignore.case = TRUE), "VA", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(dc, Column, ignore.case = TRUE), "DC", as.character(State))) 

DC <- DC %>% mutate(State = ifelse(grepl(md, Area, ignore.case = TRUE), "MD", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(va, Area, ignore.case = TRUE), "VA", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(dc, Area, ignore.case = TRUE), "DC", as.character(State))) 

DC %>% filter(is.na(State))

#now only 72,411 don't have a state designation and we can assume that they are in DC
#other ideas such as google, or simply trying each state designation may help later


#These are the top tags without a state information
DC %>% filter(is.na(State)) %>% group_by(Column) %>% summarise(count = n()) %>% arrange(desc(count))
DC %>% filter(is.na(State)) %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

#These are clear typos in the top several locations
DC <- DC %>% mutate(location = ifelse(Area != "", as.character(Area), as.character(Column))) %>%
    mutate(location = str_replace_all(location, " nw ","northwest")) %>%
    mutate(location = str_replace_all(location, "ref","")) %>%
    mutate(location = str_replace_all(location, "(nw)","")) %>%
    mutate(location = str_replace_all(location, " ne ","northeast")) %>%
    mutate(location = str_replace_all(location, " se ","southeast")) %>%
    mutate(location = str_replace_all(location, "silver spring, md","silver spring")) %>%
    mutate(location = str_replace_all(location, "alexandria, va","alexandria")) %>%
    mutate(location = str_replace_all(location, "arlington n","arlington")) %>%
    mutate(location = str_replace_all(location, "arlington, va","arlington")) %>%
    mutate(location = str_replace_all(location, "takoma park, md","takoma park"))
  


#overall 62600 locations are missing
#There are roughly 15 locations that are greater than 500 observations

DC %>% group_by(location) %>% summarise(count = n()) %>% arrange(desc(count))
DC$location <- trimws(DC$location)

```


#Run in Open Street Map

#House Number First
#Then run the small location (if no small area then large area)


#Then try the same thing through google

#This is the final dataset

```{r}
DC$Area <- tolower(DC$Area)
DC$Column <- tolower(DC$Column)
DC$Street <- tolower(DC$Street)

#DC has street information in only 45142 observations
dim(DC %>% filter(Street != ""))[1]

#DC has a Hse.no information in only 14806 observations, although, some streets have the Hse.no as a part of them
dim(DC %>% filter(Hse.No != ""))[1]

#Overall we only have 45142 observations to geocode in this part, not nearly as much as other cities
```


```{r}
DC$State[is.na(DC$State)] <- ""
DC$State[DC$State == ""] <- "DC"

DC <- DC %>% unite(Address1, c("Hse.No","Street"), sep = " ",remove = FALSE)

DC$Address1 = tolower(DC$Address1)


DC$Address1 = paste(DC$Address1, " ", sep = "")

DC = DC %>% 
  mutate(Address1 = str_replace_all(Address1, ",", " ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "[.]"," ")) %>%
  mutate(Address1 = str_replace_all(Address1, " ne ", " northeast ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "#ref!", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, " se "," southeast ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " sw "," southwest ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " nw ", " northwest ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "ny","new york")) %>% 
  mutate(Address1 = str_replace_all(Address1, "n y", "new york") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "mass ","massachusetts ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "conn ","connecticut ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " d "," D ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " d ","D") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e "," E ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e ","E") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " a "," A ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " a ","A")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b "," B ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b ","B")) %>% 
  mutate(Address1 = str_replace_all(Address1, " c "," C ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " c ","C")) %>% 
  mutate(Address1 = str_replace_all(Address1, " rd "," road ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ave "," avenue ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " st "," street ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ct "," court ")) %>%
  mutate(Address1 = str_replace_all(Address1, " pl "," place ") ) %>%
  mutate(Address1 = str_replace_all(Address1, " rd,"," road,")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ave,"," avenue,")) %>% 
  mutate(Address1 = str_replace_all(Address1, " st,"," street,")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ct,"," court,")) %>%
  mutate(Address1 = str_replace_all(Address1, " pl,"," place,") ) %>%
  mutate(Address1 = str_replace_all(Address1, "americana","american") ) %>%
  mutate(Address1 = str_replace_all(Address1, "near",""))


DC = DC %>% unite(Address, c("Address1","State"), sep = ", ",remove = FALSE)
DC$Address <- trimws(DC$Address)

DC %>% group_by(Address) %>% summarise(count = n()) %>% arrange(desc(count))


DC$Address <- sapply(DC$Address, function(x) gsub("#", "", x))
DC$Address <- sapply(DC$Address, function(x) gsub("near", "", x))
DC$Address <- gsub("[.]", "", DC$Address)
DC$Address[which(DC$Address  == ", DC")] <- ""
DC$Address[which(DC$Address  == ", MD")] <- ""
DC$Address[which(DC$Address  == ", VA")] <- ""

DC %>% group_by(Address) %>% summarise(count = n()) %>% arrange(desc(count))

#In total we only have 45499 observations to geocode based on its street
dim(DC)[1] - dim(DC %>% filter(Address == ""))[1]

```


Starting off with the first address set

```{r}
#We start with the 45499 that have observations
#Then we join them with the no address columns and move on

AddressGroup = DC[DC$Address != "",]

nonAddressGroup = DC[DC$Address == "",]
nonAddressGroup = nonAddressGroup %>% add_column(latitude = NA) %>% add_column(longitude = NA) %>% mutate(latitude = as.double(latitude)) %>% mutate(longitude = as.double(longitude))
```


```{r}
geocodedAddressDC <- tidygeocoder::geocode(.tbl = AddressGroup, address = Address, method = "osm", lat = latitude, long = longitude)

#join the files back together and save them 
geocodedAllDC = rbind(geocodedAddressDC, nonAddressGroup)
save(geocodedAllDC, file = "allDC.RData")

geocodedAllDC %>% filter(!is.na(latitude))
```

```{r}
load(file = "allDC.RData")
```

```{r}
geocodedDCFound <- geocodedAllDC %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
geocodedDCReDo <- geocodedAllDC %>% filter(is.na(latitude) | !((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
geocodedDCFound
geocodedDCReDo
```

Now we geocode the set that we did not find 'geocodedDCReDo'. 

```{r}
geocodedDCReDo$State[is.na(geocodedDCReDo$State)] <- ""
geocodedDCReDo <- geocodedDCReDo %>% select(-latitude, -longitude)
geocodedDCReDo$State[geocodedDCReDo$State == ""] <- "DC"

geocodedDCReDo <- geocodedDCReDo %>% unite(AddressLocation, c("location","State"), sep = ", ",remove = FALSE)
geocodedDCReDo$AddressLocation <- gsub("[.]", "", geocodedDCReDo$AddressLocation)
geocodedDCReDo$AddressLocation <- gsub("#", "", geocodedDCReDo$AddressLocation)
geocodedDCReDo$AddressLocation <- gsub("!", "", geocodedDCReDo$AddressLocation)

#We want more concise information than simply the state or the city of DC, so this information is effectively null
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "dc, DC"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "virginia, VA"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "maryland, MD"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == ", DC"] <- ""
geocodedDCReDo
```


```{r}
DC20 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[1:20000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC20, file = "DC20.RData")

DC40 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[20001:40000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC40, file = "DC40.RData")

DC60 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[40001:60000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC60, file = "DC60.RData")

DC80 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[60001:80000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC80, file = "DC80.RData")

```


```{r}
load(file = "DC20.RData")
load(file = "DC40.RData")
load(file = "DC60.RData")
load(file = "DC80.RData")

DC20
DC40
DC60
DC80 <- DC80[1:9764,]

full = rbind(DC20,DC40,DC60,DC80)
save(full, file = "full.RData")

load(file = "full.RData")

#full = full %>% mutate(latitude = latitude1) %>% mutate(longitude = longitude1) %>% select(-latitude1, -longitude1)

found <- full %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
notFound <- full %>% filter(is.na(latitude) | !((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )

found
notFound

geocodedDCFound = geocodedDCFound %>% add_column(AddressLocation = "", .before = "State")

DCGeocoded = rbind(geocodedDCFound,found)

notFound %>% filter(is.na(latitude)) %>% filter(Address == "")




```

Second Pass at addresses

```{r}

notFound$Address1 = paste(notFound$Address1, " ", sep = "")

notFound <- notFound %>% 
  mutate(Address1 = str_replace_all(Address1, ",", " ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "[.]"," ")) %>%
  mutate(Address1 = str_replace_all(Address1, " northeast ", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, "#ref!", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, " se "," southeast ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " sw "," southwest ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " nw ", " northwest ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "ny","new york")) %>% 
  mutate(Address1 = str_replace_all(Address1, "n y", "new york") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " n j ", " new jersey ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "mass ","massachusetts ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "conn ","connecticut ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " d "," D ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " d ","D") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e "," E ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e ","E") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " a "," A ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " a ","A")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b "," B ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b ","B")) %>% 
  mutate(Address1 = str_replace_all(Address1, " c "," C ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " c ","C")) %>% 
  mutate(Address1 = str_replace_all(Address1, " rd "," road ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ave "," avenue ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " street ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ct "," court ")) %>%
  mutate(Address1 = str_replace_all(Address1, " pl "," place ") ) %>%
  mutate(Address1 = str_replace_all(Address1, "americana","american") ) %>%
  mutate(Address1 = str_replace_all(Address1, "near","")) 


notFound = notFound %>% unite(Address, c("Address1","State"), sep = ", ",remove = FALSE) %>% select(-latitude,-longitude)
notFound$Address <- trimws(notFound$Address)
notFound

```

```{r}
DCSecondPassAddress <- tidygeocoder::geocode(.tbl = notFound, address = Address, method = "osm", lat = latitude, long = longitude)
save(DCSecondPassAddress, file = "DCSecondPassAddress.RData")
```

```{r}
load(file = "DCSecondPassAddress.RData")
found <- DCSecondPassAddress %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
notFound <- DCSecondPassAddress %>% filter(is.na(latitude) | !((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )

found
notFound
```

```{r}
DCGeocoded = rbind(DCGeocoded,found)
save(DCGeocoded, file = "DCGeocoded.RData")
```



```{r}

notFound$Address1 = paste(notFound$Address1, " ", sep = "")

notFound <- notFound %>% 
  mutate(Address1 = str_replace_all(Address1, ",", " ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "[.]"," ")) %>%
  mutate(Address1 = str_replace_all(Address1, " northeast ", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, "#ref!", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, " southeast ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " southwest ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " northwest ", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, "ny","new york")) %>% 
  mutate(Address1 = str_replace_all(Address1, "n y", "new york") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " n j ", " new jersey ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "mass ","massachusetts ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "conn ","connecticut ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " f "," F ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " d "," D ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " h "," H street") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " u "," U street ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e ","E") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "northwest","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " a ","A")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b "," B ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "r i  ","rhode island ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " F "," F Street ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " c ","C")) %>% 
  mutate(Address1 = str_replace_all(Address1, " rd "," road ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ave "," avenue ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " street ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ct "," court ")) %>%
  mutate(Address1 = str_replace_all(Address1, " pl "," place ") ) %>%
  mutate(Address1 = str_replace_all(Address1, "americana","american") ) %>%
  mutate(Address1 = str_replace_all(Address1, "near","")) 

notFound$State <- trimws(notFound$State)
notFound = notFound %>% mutate(State = ifelse(State == "DC", "Washington, DC", as.character(State)) )
notFound = notFound %>% unite(Address, c("Address1","State"), sep = " ",remove = FALSE) %>% select(-latitude,-longitude)
notFound$Address <- trimws(notFound$Address)
notFound
```




```{r}
DCSecondPassAddress <- tidygeocoder::geocode(.tbl = notFound, address = Address, method = "osm", lat = latitude, long = longitude)
save(DCSecondPassAddress, file = "DCSecondPassAddress.RData")
```


```{r}
load(file = "DCSecondPassAddress.RData")
found <- DCSecondPassAddress %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
notFound <- DCSecondPassAddress %>% filter( is.na(latitude) | !((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )

found
save(notFound, file = "DCnotFound.RData")
```

```{r}
DCGeocoded = rbind(DCGeocoded,found)
save(DCGeocoded, file = "DCGeocoded.RData")
```



#two more attempts, one with the census geocoder and one with location used.

```{r}
notFound$location = notFound$location %>% replace_na("")
notFound %>% group_by(AddressLocation) %>% summarise(count = n()) %>% arrange(desc(count))
```

```{r}

notFound$Address1 = paste(notFound$Address1, " ", sep = "")

notFound <- notFound %>% 
  mutate(Address1 = str_replace_all(Address1, ",", " ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "[.]"," ")) %>%
  mutate(Address1 = str_replace_all(Address1, " # ", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, "#ref!", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ! ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " southwest ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " northwest ", "")) %>% 
  mutate(Address1 = str_replace_all(Address1, "ny","new york")) %>% 
  mutate(Address1 = str_replace_all(Address1, "n y", "new york") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " n j ", " new jersey ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "mass ","massachusetts ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "conn ","connecticut ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " g "," G ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " & "," and ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "'"," ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "-","") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " h "," H street") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " u "," U street ") ) %>% 
  mutate(Address1 = str_replace_all(Address1, " e ","E") ) %>% 
  mutate(Address1 = str_replace_all(Address1, "northwest","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " a ","A")) %>% 
  mutate(Address1 = str_replace_all(Address1, " b "," B ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " r i  ","rhode island ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "\" ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " \' ","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " rd "," road ")) %>% 
  mutate(Address1 = str_replace_all(Address1, " ave "," avenue ")) %>% 
  mutate(Address1 = str_replace_all(Address1, "/","")) %>% 
  mutate(Address1 = str_replace_all(Address1, " \\)","")) %>%
  mutate(Address1 = str_replace_all(Address1, "\\(","") ) %>%
  mutate(Address1 = str_replace_all(Address1, "^","") ) %>%
  mutate(Address1 = str_replace_all(Address1, "#","")) 

notFound$State <- trimws(notFound$State)
notFound = notFound %>% mutate(State = ifelse(State == "DC", "Washington, DC", as.character(State)) )
notFound = notFound %>% unite(Address, c("Address1","State"), sep = " ",remove = FALSE) %>% select(-latitude,-longitude)
notFound$Address <- trimws(notFound$Address)
notFound
```

```{r}
DCThirdPassAddress <- tidygeocoder::geocode(.tbl = notFound[1:500,], address = Address, method = "census", lat = latitude, long = longitude)
DCThirdPassAddress %>% filter(!is.na(latitude))
save(DCThirdPassAddress, file = "DCThirdPassAddress.RData")
```

```{r}
load(file = "DCThirdPassAddress.RData")
found <- DCThirdPassAddress %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )
notFound <- DCThirdPassAddress %>% filter( is.na(latitude) | !((latitude > 38.3 & latitude < 39.15) & (longitude > -78.35 & longitude < -76.30)) )

found
notFound
```

```{r}
DCGeocoded = rbind(DCGeocoded,found)
save(DCGeocoded, file = "DCGeocoded.RData")
notFound
```


Bring the entire dataset back together.
Mark which columns were generated from google.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r} 
map <- get_map(location = 'DC', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = DCGeocoded, mapping = aes(x = longitude, y = latitude, color = factor(location)), size = 0.1) + theme(legend.position = "none")

```

