---
title: "All Geocoded DC"
author: "Bill Lang"
date: "11/1/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
```


```{r}
load(file = "DC.RData")
load(file = "DChandcheck.RData")

```



```{r}
DC
DChandcheck

DC %>% filter(Area != "")
DC %>% group_by(Column) %>% summarise(count = n()) %>% arrange(desc(count))
DC %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

#70,785 with and 63,725 without area, 

DChandcheck <- DChandcheck %>% mutate(Area = ï..Area) %>% select(Area,State) %>% distinct() %>% filter(State != "")

DChandcheck %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

DC <- DC %>% mutate(Area = tolower(Area)) %>% left_join(DChandcheck, by = 'Area') 
DC %>% filter(is.na(State))
```


```{r}
DC$Column <- tolower(DC$Column)
DC$Column <- gsub("[.]", "", DC$Column)
DC$Column <- trimws(DC$Column)

DC$Area <- tolower(DC$Area)
DC$Area <- gsub("[.]", "", DC$Area)
DC$Area <- trimws(DC$Area)

md = c("maryland|md|montgomery|prince george's|mont|prince georges|prince george|bethesda|silver spring|college park|prince geo|princegeo|princ geo|annapolis|chevy chase|rockville|gaithersburg")
va = c("virginia|va|alexandria|fairfax|arlington|falls church")
dc = c("dc|d c|district of columbia|washington|district columbia|georgetown")

DC <- DC %>% mutate(State = ifelse(grepl(md, Column, ignore.case = TRUE), "MD", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(va, Column, ignore.case = TRUE), "VA", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(dc, Column, ignore.case = TRUE), "DC", as.character(State))) 

DC <- DC %>% mutate(State = ifelse(grepl(md, Area, ignore.case = TRUE), "MD", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(va, Area, ignore.case = TRUE), "VA", as.character(State))) 
DC <- DC %>% mutate(State = ifelse(grepl(dc, Area, ignore.case = TRUE), "DC", as.character(State))) 

DC %>% filter(is.na(State))

#now only 72,411 don't have a state designation and we can assume that they are in DC
#other ideas such as google, or simply trying each state designation may help later


#These are the top tags without a state information
DC %>% filter(is.na(State)) %>% group_by(Column) %>% summarise(count = n()) %>% arrange(desc(count))
DC %>% filter(is.na(State)) %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))

#These are clear typos in the top several locations
DC <- DC %>% mutate(location = ifelse(Area != "", as.character(Area), as.character(Column))) %>%   mutate(location = case_when(
    str_detect(location, "nw") ~ "northwest",
    str_detect(location, "#ref!") ~ "",
    str_detect(location, "sw") ~ "southwest",
    str_detect(location, "(nw)") ~ "",
    str_detect(location, "ne") ~ "northeast",
    str_detect(location, "se") ~ "southeast",
    str_detect(location, "silver spring, md") ~ "silver spring",
    str_detect(location, "arlington n") ~ "arlington",
    str_detect(location, "alexandria, va") ~ "alexandria",
    str_detect(location, "arlington, va") ~ "arlington",
    str_detect(location, "takoma park, md") ~ "takoma park",
    TRUE ~ location
    )
  )

#overall 61,466 locations are missing
#There are roughly 15 locations that are greater than 500 observations

DC %>% group_by(location) %>% summarise(count = n()) %>% arrange(desc(count))
DC$location <- trimws(DC$location)

```


#Run in Open Street Map

#House Number First
#Then run the small location (if no small area then large area)


#Then try the same thing through google

#This is the final dataset

```{r}
DC$Area <- tolower(DC$Area)
DC$Column <- tolower(DC$Column)
DC$Street <- tolower(DC$Street)

#DC has street information in only 45142 observations
dim(DC %>% filter(Street != ""))[1]

#DC has a Hse.no information in only 14806 observations, although, some streets have the Hse.no as a part of them
dim(DC %>% filter(Hse.No != ""))[1]

#Overall we only have 45142 observations to geocode in this part, not nearly as much as other cities
```


```{r}
DC$State[is.na(DC$State)] <- ""
DC$State[DC$State == ""] <- "DC"

DC <- DC %>% unite(Address1, c("Hse.No","Street"), sep = " ",remove = FALSE)

DC <- DC %>% unite(Address, c("Address1","State"), sep = ", ",remove = FALSE)
DC$Address <- trimws(DC$Address)

DC %>% group_by(Address) %>% summarise(count = n()) %>% arrange(desc(count))

DC <- DC %>% mutate(Address = case_when(
    str_detect(location, "nw") ~ "northwest",
    str_detect(location, "sw") ~ "southwest",
    str_detect(location, "ne") ~ "northeast",
    str_detect(location, "se") ~ "southeast",
    TRUE ~ location
    )
  )



DC$Address <- sapply(DC$Address, function(x) gsub("#", "", x))
DC$Address <- sapply(DC$Address, function(x) gsub("near", "", x))
DC$Address <- gsub("[.]", "", DC$Address)
DC$Address[which(DC$Address  == ", DC")] <- ""
DC$Address[which(DC$Address  == ", MD")] <- ""
DC$Address[which(DC$Address  == ", VA")] <- ""

DC %>% group_by(Address) %>% summarise(count = n()) %>% arrange(desc(count))

#In total we only have 45499 observations to geocode based on its street
dim(DC)[1] - dim(DC %>% filter(Address == ""))[1]

```


Starting off with the first address set

```{r}
#We start with the 45499 that have observations
#Then we join them with the no address columns and move on

AddressGroup = DC[DC$Address != "",]

nonAddressGroup = DC[DC$Address == "",]
nonAddressGroup = nonAddressGroup %>% add_column(latitude = NA) %>% add_column(longitude = NA) %>% mutate(latitude = as.double(latitude)) %>% mutate(longitude = as.double(longitude))

geocodedAddressDC <- tidygeocoder::geocode(.tbl = AddressGroup, address = Address, method = "osm", lat = latitude, long = longitude)

#join the files back together and save them 
geocodedAllDC = rbind(geocodedAddressDC, nonAddressGroup)
save(geocodedAllDC, file = "allDC.RData")

geocodedAllDC %>% filter(is.na(latitude))
```

```{r}
load(file = "allDC.RData")
```

```{r}
geocodedDCFound <- geocodedAllDC %>% filter(!is.na(latitude)) %>% filter( ((latitude > 38.3 & latitude < 40.0) & (longitude > -78.35 & longitude < -76.30)) )
geocodedDCReDo <- geocodedAllDC %>% filter(is.na(latitude) | !((latitude > 38.3 & latitude < 40.0) & (longitude > -78.35 & longitude < -76.30)) )
geocodedDCFound
geocodedDCReDo
```

Now we geocode the set that we did not find 'geocodedLAReDo'. I use a google maps quote for this specifically, to get the best results. Google's system works far better for interpreting ambiguous inputs.

```{r}
geocodedDCReDo$State[is.na(geocodedDCReDo$State)] <- ""
geocodedDallasReDo <- geocodedDallasReDo %>% select(-latitude, -longitude)
geocodedDCReDo$State[geocodedDCReDo$State == ""] <- "DC"

geocodedDCReDo <- geocodedDCReDo %>% unite(AddressLocation, c("location","State"), sep = ", ",remove = FALSE)
geocodedDCReDo$AddressLocation <- gsub("[.]", "", geocodedDCReDo$AddressLocation)

#We want more concise information than simply the state or the city of DC, so this information is effectively null
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "dc"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "virginia"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == "maryland"] <- ""
geocodedDCReDo$AddressLocation[geocodedDCReDo$AddressLocation  == ", DC"] <- ""
geocodedDCReDo
```

```{r}
DC20 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[1:20000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC20, file = "DC20.RData")

DC40 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[20001:40000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC40, file = "DC40.RData")

DC60 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[40001:60000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC60, file = "DC60.RData")

DC80 <- tidygeocoder::geocode(.tbl = geocodedDCReDo[60001:80000,], address = AddressLocation, method = "osm", lat = latitude, long = longitude)
save(DC80, file = "DC80.RData")

```


```{r}
load(file = "DC20.RData")
load(file = "DC40.RData")
load(file = "DC60.RData")
load(file = "DC80.RData")
load(file = "DCRest.RData")

DC20
DC40
DC60
DC80 <- DC80[1:9764,]

full = rbind(DC20,DC40,DC60,DC80)
save(full, file = "full.RData")
load(file = "full.RData")

full = full %>% mutate(latitude = latitude1) %>% mutate(longitude = longitude1) %>% select(-latitude1, -longitude1)
geocodedDCFound <- geocodedDCFound %>% add_column(AddressLocation = "", .before = "State")
DCGeocoded = rbind(geocodedDCFound,full)

newDC %>% filter(is.na(latitude)) %>% filter(Address == "")
```


```{r}
save(DCGeocoded, file = "DCGeocoded.RData")
```







```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```

```{r}
#SecondDallas <- ggmap::mutate_geocode(geocodedDallasReDo, Address)
#save(SecondDallas, file = "SecondDallas.RData")
```


```{r}
load(file = "secondDallas.RData")
SecondDallas <- SecondDallas %>% mutate(latitude = lat) %>% mutate(longitude = lon) %>% select(-lat,-lon)
```

Bring the entire dataset back together.
Mark which columns were generated from google.

```{r}
geocodedDallasFound <- geocodedDallasFound %>% mutate(google = 0)
SecondDallas <- SecondDallas %>% mutate(google = 1)
dallasGeocoded <- rbind(geocodedDallasFound, SecondDallas)


save(dallasGeocoded, file = "dallasGeocoded.RData")
```



```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```



```{r} 
map <- get_map(location = 'DC', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = newDC, mapping = aes(x = longitude, y = latitude, color = factor(location)), size = 0.1) + theme(legend.position = "none")

```

