---
title: "Training Random Forest DC"
author: "Bill Lang"
date: "11/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```



Reading in file.

```{r}
load(file = "cleanDC.RData")
cleanDC
```

Removing areas with no information. 

```{r}
cleanDC$location[cleanDC$location  == "dc"] <- ""
cleanDC$location[cleanDC$location  == "virginia"] <- ""
cleanDC$location[cleanDC$location  == "maryland"] <- ""
cleanDC$location[cleanDC$location  == "se"] <- "southeast"
```

Finding the top 50 labeled areas.

```{r}
cleanDC$location <- tolower(cleanDC$location)
tbl <- cleanDC %>% group_by(location) %>% summarise(count = n()) %>% arrange(desc(count)) %>% filter(location != "")
listOfAreas <- tbl[1:25,]$location
listOfAreas
save(listOfAreas, file = "AreasDC.RData")
```

Find the observations with a top 50 area. 

```{r}
DCTop <- DCData %>% filter(location %in% listOfAreas)

#saving this file for the export dataset
DCTop %>% group_by(location) %>% summarise(count = n())

save(DCTop, file = "DCTop.RData")
```


This model is built on a random shuffle of the data and validated by holding out 20% of the dataset. 
 
```{r}
load(file = "DCTop.RData")

DCTop$location = as.character(DCTop$location)
DCTop$location = as.factor(DCTop$location)

modelData <- DCTop 
set.seed(344)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.8)
modelTrain <- modelData[train,]
modelTest <- modelData[-train,]
```


```{r}
bag <- randomForest(location ~ latitude + longitude + Year + capitalizedPrice + Total.rooms.estimation, data = modelTrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(bag, newdata = modelTest)
misclassRate <- mean(yhat.rf != modelTest$location)
misclassRate
```


We can then map the results using the ggmaps package below to manuely search for any errors.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```


```{r} 
map <- get_map(location = 'DC', zoom = 8, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(location)), size = 0.1) + theme(legend.position = "none")
```


Full Model

Using all the available data we construct a full model to use for the rest of the analysis. 

```{r}
fullModel <- randomForest(location ~ latitude + longitude + Year + capitalizedPrice + Total.rooms.estimation, data = modelData, ntree = 1000, mtry = 2, importance = TRUE)
```































