---
title: "All Geodcoded Philadelphia"
author: "Bill Lang"
date: "2/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggmap)
```


```{r}
load(file = "Detroit.RData")
detroit

detroit %>% filter(Area != "")
detroit %>% group_by(Column.Location) %>% summarise(count = n()) %>% arrange(desc(count))
detroit %>% group_by(Area) %>% summarise(count = n()) %>% arrange(desc(count))
detroit %>% filter(Street != "")

#24433 with and 53655 without area, Column.Loation has just Dallas
#34,355 full address, 59,447 with street
```

Dataset Specific preparation

Run in Open Street Map
House Number First
Then run the small location (if no small area then large area)

```{r}
detroit$Area <- tolower(detroit$Area)
detroit$Column.Location <- tolower(detroit$Column.Location)
detroit$Street <- tolower(detroit$Street)


detroit <- detroit %>% mutate(location = ifelse(Area != "", as.character(Area), as.character(Column.Location))) %>% mutate(location = str_replace_all(location, "detroit", "")) %>%
  mutate(location = str_replace_all(location, "detriot", ""))

detroit %>% filter(location != "")
#28,064 not blank location


#We can build the addres column to geocode

detroit <- detroit %>% unite(Address, c("Hse.No","Street", "location"), sep = " ",remove = FALSE)
detroit$Address <- paste(detroit$Address, ", Detroit")
detroit$Address <- trimws(detroit$Address)

detroit = detroit %>% 
  mutate(Address = str_replace_all(Address, "#", "")) %>% 
  mutate(Address = str_replace_all(Address, "[.]"," ")) %>%
  mutate(Address = str_replace_all(Address, " ne ", " northeast ")) %>% 
  mutate(Address = str_replace_all(Address, "#ref!", "")) %>% 
  mutate(Address = str_replace_all(Address, " se "," southeast ")) %>% 
  mutate(Address = str_replace_all(Address, " sw "," southwest ")) %>% 
  mutate(Address = str_replace_all(Address, " nw ", " northwest ")) %>% 
  mutate(Address = str_replace_all(Address, "ny","new york")) %>% 
  mutate(Address = str_replace_all(Address, "n y", "new york") ) %>% 
  mutate(Address = str_replace_all(Address, "mass ","massachusetts ")) %>% 
  mutate(Address = str_replace_all(Address, "conn ","connecticut ") ) %>% 
  mutate(Address = str_replace_all(Address, " rd "," road ")) %>% 
  mutate(Address = str_replace_all(Address, " ave "," avenue ")) %>% 
  mutate(Address = str_replace_all(Address, " st "," street ")) %>% 
  mutate(Address = str_replace_all(Address, " ct "," court ")) %>%
  mutate(Address = str_replace_all(Address, " pl "," place ") ) %>%
  mutate(Address = str_replace_all(Address, " rd,"," road,")) %>% 
  mutate(Address = str_replace_all(Address, " ave,"," avenue,")) %>% 
  mutate(Address = str_replace_all(Address, " st,"," street,")) %>% 
  mutate(Address = str_replace_all(Address, " ct,"," court,")) %>%
  mutate(Address = str_replace_all(Address, " pl,"," place,") ) %>%
  mutate(Address = str_replace_all(Address, "americana","american") ) %>%
  mutate(Address = str_replace_all(Address, "near",""))
detroit
```

Starting off with the first address set

```{r}
geocodedAllDetroit <- tidygeocoder::geocode(.tbl = detroit, address = Address, method = "osm", lat = latitude, long = longitude)
geocodedAllDetroit
save(geocodedAllDetroit, file = "allDetroit.RData")

geocodedAllDetroit %>% filter(!is.na(latitude))
```

```{r}
load(file = "allDetroit.RData")
geocodedAllDetroit
```

```{r}
geocodedDetroitFound <- geocodedAllDetroit %>% filter(!is.na(latitude)) %>% filter( ((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitReDo <- geocodedAllDetroit %>% filter(is.na(latitude) | !((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitReDo
geocodedDetroitFound 
```

We redo the geocoding with a new address for each by removing the "location" data that was put in before.

```{r}
geocodedDetroitReDo <- geocodedDetroitReDo %>% unite(Address, c("Hse.No","Street"), sep = " ",remove = FALSE)
geocodedDetroitReDo$Address <- paste(geocodedDetroitReDo$Address, ",Detroit") 
geocodedDetroitReDo <- geocodedDetroitReDo %>% select(-latitude, -longitude)
geocodedDetroitReDo
```

```{r}
secondDetroit <- tidygeocoder::geocode(.tbl = geocodedDetroitReDo, address = Address, method = "osm", lat = latitude, long = longitude)
secondDetroit
save(secondDetroit, file = "secondDetroit.RData")
secondDetroit %>% filter(!is.na(latitude))
```

```{r}
load(file = "secondDetroit.RData")
secondDetroit
```

```{r}
geocodedDetroitFound2 <- secondDetroit %>% filter(!is.na(latitude)) %>% filter( ((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitReDo2 <- secondDetroit %>% filter(is.na(latitude) | !((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitFound2
geocodedDetroitReDo2
```

Add the newly found rows into the entire dataset

```{r}
detroitGeocoded <- rbind(geocodedDetroitFound, geocodedDetroitFound2)
detroitGeocoded
```

```{r}
geocodedDetroitReDo2
```



We redo the geocoding with a new address for each by removing the "location" data that was put in before.

```{r}
geocodedDetroitReDo2 <- geocodedDetroitReDo2 %>% unite(Address, c("Hse.No","Street"), sep = " ",remove = FALSE)
geocodedDetroitReDo2$Address <- paste(geocodedDetroitReDo2$Address, ",Michigan") 
geocodedDetroitReDo2 <- geocodedDetroitReDo2 %>% select(-latitude, -longitude)
geocodedDetroitReDo2
```

```{r}
thirdDetroit <- tidygeocoder::geocode(.tbl = geocodedDetroitReDo2, address = Address, method = "osm", lat = latitude, long = longitude)
thirdDetroit
save(thirdDetroit, file = "thirdDetroit.RData")
secondDetroit %>% filter(!is.na(latitude))
```

```{r}
load(file = "thirdDetroit.RData")
thirdDetroit
```

```{r}
geocodedDetroitFound3 <- thirdDetroit %>% filter(!is.na(latitude)) %>% filter( ((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitReDo3 <- thirdDetroit %>% filter(is.na(latitude) | !((latitude > 42 & latitude < 43) & (longitude > -84 & longitude < -82)) )
geocodedDetroitReDo3
geocodedDetroitFound3
```

Add the newly found rows into the entire dataset

```{r}
detroitGeocoded <- rbind(detroitGeocoded, geocodedDetroitFound3)
detroitGeocoded
```

```{r}
notGeocoded = geocodedDetroitReDo3
notGeocoded
save(notGeocoded, file = "notGeocoded.RData")
```

```{r}
save(detroitGeocoded, file = "detroitGeocoded.RData")
```



```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```


```{r} 
map <- get_map(location = 'Detroit', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = detroitGeocoded, mapping = aes(x = longitude, y = latitude, color = factor(location)), size = 0.1) + theme(legend.position = "none")
```

