---
title: "Driver File"
author: "Bill Lang"
date: "4/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This first portion just brings together all of our data, it was preiovusly split by geocoded and not geocoded but this functions handle and encourage that situation.

```{r}
library(tidyverse)
load(file = "dallasGeocodedNotFound.RData")
geocodedDallasNotFound = geocodedDallasNotFound %>% select(-c(X,X.1))
geocodedDallasNotFound


load(file = "dallasGeocoded2.RData")
dallasGeocoded

data = plyr::rbind.fill(dallasGeocoded,geocodedDallasNotFound)
data
```


Load the packages

```{r}
loadPackages()
```

```{r}
classified = callSingleForest(data, locationCount = 20)
classified
```


```{r}
classified = callTripleForest(data, locationCount = 20)
classified
```

```{r}
classified = callSingleandTriple(data, locationCount = 20)
classified
```

```{r}

classified = callNPeriodForest(data, locationCount = 20, splitBy = 5)
classified
```





Animations. 

Install and/or load the packages.

```{r}
loadPackagesAnimations()
```

Call the map.(e.g. location = "city")

```{r}
map <- get_map(location = 'Dallas', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')
```

Call the render on the data you are working with. Can make use of all the parameters created in `AnimationFunctions.R` 

```{r}
anim = callRender(dallasData, minYear = 0, maxYear = 2100, )
```

Call animate, renderer needs to be magick_renderer right now since there are bugs with the default package (as of March 2021). 
This can take a long time. See all parameters by running `?animate`.

```{r}
animate(anim, renderer = magick_renderer(), duration = 50, fps = 10)
```



