---
title: "Training Random Forest Dallas"
author: "Bill Lang"
date: "10/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygeocoder)
library(ggmap)
library(randomForest)
```



Reading in file.

```{r}
load(file = "cleanDallas.RData")
dallasData
```

Removing areas with no information. 

```{r}
dallasData <- dallasData %>% filter(location != "")
```

Finding the top 50 labeled areas.

```{r}
dallasData$location <- tolower(dallasData$location)
tbl <- dallasData %>% group_by(location) %>% summarise(count = n()) %>% arrange(desc(count))
listOfAreas <- tbl[1:15,]$location
listOfAreas
save(listOfAreas, file = "AreasDallas.RData")
```

Find the observations with a top 50 area. 

```{r}
dallasAddress <- dallasData %>% filter(Area %in% listOfAreas)

#saving this file for the export dataset
dallasAddress

save(dallasAddress, file = "dallasTop.RData")
```


This model is built on a random shuffle of the data and validated by holding out 20% of the dataset. 
 
```{r}
dallasAddress$location = as.factor(dallasAddress$location)

modelData <- dallasAddress 
set.seed(343)
shuf <- sample(nrow(modelData))
modelData <- modelData[shuf,]
train <- sample(nrow(modelData)*.8)
modelTrain <- modelData[train,]
modelTest <- modelData[-train,]
```


```{r}
bag <- randomForest(location ~ latitude + longitude + Year +Total.rooms.estimation , data = modelTrain, ntree = 1000, importance = TRUE)
yhat.rf <- predict(bag, newdata = modelTest)
misclassRate <- mean(yhat.rf != modelTest$location)
misclassRate
```


We can then map the results using the ggmaps package below to manuely search for any errors.

```{r}
k <- "AIzaSyDNMoGGfgl9f5KtGCnp9BegNb7ZDqPu7gg"
register_google(key = k)
```


```{r} 
map <- get_map(location = 'Dallas', zoom = 10, maptype = "terrain-background", source = 'google', color = 'color')
ggmap(map) + geom_point(data = modelData, mapping = aes(x = longitude, y = latitude, color = factor(location)), size = 0.1) + theme(legend.position = "none")

```


Full Model

Using all the available data we construct a full model to use for the rest of the analysis. 

```{r}
fullModel <- randomForest(location ~ latitude + longitude + Year +Total.rooms.estimation , data = modelData, ntree = 1000, mtry = 2, importance = TRUE)
```































